### 2021-04-06 README.Rmd
update readme

The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with.
Binder uses rocker-project.org Docker images to ensure a consistent and reproducible computational environment.
These Docker images can also be used locally.

You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip).
After unzipping:

-   open the `.Rproj` file in RStudio
-   something about `renv`
-   something about `targets::tar_make()` and `targets::tar_visnetwork()` <!-- -   run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file). --> <!-- -   finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console -->

>>>>

<!-- The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with. -->

<!-- Binder uses rocker-project.org Docker images to ensure a consistent and reproducible computational environment. -->

<!-- These Docker images can also be used locally. -->

You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip).

To run the compendium and reproduce all outputs:

-   Open the `.Rproj` file in RStudio
-   Install the `renv` package if it's not already installed and run `renv::restore()` to install all package dependencies. (I'm not actually sure that this step is necessar. Should auto-load because of .Rprofile.)
-   Run `targets::tar_make()` to run all code and produce all outputs.
